\section{Evaluation / demonstration}
	The profiler should give one the ability to run DNA with an optimized combination of data
	structures. In this section, we want to demonstrate the capabilites of the recommender.
	After having already evaluated some very simple cases in section \ref{sec:performance},
	we additionally chose two more scenarios for this to evaluate the recommender. We
	initially select data structures for the global node and edge list and the node-local
	edge list as bad as possible to demonstrate the later enhancements.
	
	In the first scenario, the graph should grow from batch to batch by 1000 nodes and 2000
	edges without removing anything. Before each graph update, the degree distribution is
	refreshed. We store all lists in arrays as it is expensive to add entries to an array:
	the first step is checking whether the element is already contained in that array by
	iterating over the whole array (linear complexity - other data structures can do this
	with static complexity), the second step is adding the element. The calculated complexity
	for one example run with this data structure combination is $549770*O(1) + 324688*O(d) +
	295205*O(E)$, the runtime can be averaged to $\sim 9000$ msec. Using arrays to store the
	global node list and HashSets for both edge lists, the complexity can be estimated to
	$1007319*O(1)$. Using the recommended combination leads to a complexity of $844477*O(1)$
	and an averaged runtime of $\sim 1745$ msec ($- 80\%$).
		
	In the second scenario, it should shrink from a graph with 2 000 nodes and 3 000
	edges by 100 nodes and 150 edges per batch, computing shortest paths alongside. Using the
	initial data structure combination, the complexity of an example run is $74937234*O(1) +
	36012*O(d) + 24012*O(N) + 9006*O(E)$, the averaged runtime is $\sim 10690$ msec. The
	recommended data structures (here: \texttt{DArray} / \texttt{DHashMap} /
	\texttt{DHashSet}) lead to an estimated complexity of $75075849*O(1) + 1863*O(E)$. Using
	this combination leads to a complexity of $75231610*O(1) + 1858*O(E)$ for an example run
	and an averaged runtime of $\sim 14540$ msec. We also see this correlation in evaluations
	with larger and smaller graphs. Other recommended combinations did neither perform
	noticeable better than the initial combination.
	
	
